Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-17 paper/paper.tex
put in exact numbers for rules

\begin{enumerate}
    \item If \IncompleteLAD removes at least \SI{28}{\percent} of the pairs,
        and at least \SI{94}{\percent} of the values from at least one domain,
        then pick \PathLAD.
    \item If the target has at least $610$ vertices, and if the maximum
        distance between any two pattern vertices is at most $8$, and if the
        pattern is not regular, and if the time taken to compute the
        distance-based features on the target graph is no more than
        \SI{1277}{\ms}, then pick \PathLAD.
    \item If \IncompleteLAD filtering removed at least \SI{6}{\percent} of
        possible pairs, and if less than \SI{85}{\percent} of the pattern
        vertices are within distance 2 of each other, then pick \PathLAD.
    \item Otherwise, pick \GlasgowTwo.
\end{enumerate}

>>>>

\begin{enumerate}
    \item If \IncompleteLAD removes at least \SI{28.014755}{\percent} of the pairs,
        and at least \SI{94.117645}{\percent} of the values from at least one domain,
        then pick \PathLAD.
    \item If the target has at least $610$ vertices, and if the maximum
        distance between any two pattern vertices is at most $8$, and if the
        pattern is not regular, and if the time taken to compute the
        distance-based features on the target graph is no more than
        \SI{1277}{\ms}, then pick \PathLAD.
    \item If \IncompleteLAD filtering removed at least \SI{5.904644}{\percent} of
        possible pairs, and if less than \SI{84.6565}{\percent} of the pattern
        vertices are within distance 2 of each other, then pick \PathLAD.
    \item Otherwise, pick \GlasgowTwo.
\end{enumerate}
